\section{Segmentation performance}
\label{sect:perf}

This section compares the performance of each type of proxy model to the teacher model.
The SAD, ND, MD, and OSD performances are presented in the table \ref*{tab:seg_results}.

The teacher's performance is considered the baseline.
The proxy models are expected to reach similar performance as the teacher.

The spectrogram-based system (spec.) shows 96.3\% and 95.5\% F1-score on the SAD task on DiHard and AragonRadio respectively.
This represents a little degradation concerning the teacher.
The ND (73.0\%) and MD (87.6\%) are also degraded by an absolute -5,6\% compared to the teacher.
The strongest degradation is observed on the OSD with a 40.1\% F1-score.
The spectrogram-based model degrades the segmentation performance.
However, this result is expected since the teacher is trained on Wavlm pre-trained features which perform better than the spectrogram.
Considering the cost of Wavlm pretraining and the inference time, the spectrogram-based model offers a convincing performance.
% Add inference time?

\begin{table}[ht]
    \centering
    \begin{tabular}{lccccc}
        \toprule
         & \multicolumn{3}{c}{Aragon Radio} & \multicolumn{2}{c}{DiHard III} \\
         \cmidrule{2-4}
         \cmidrule{5-6}
         Model & SAD & ND & MD & SAD & OSD \\  
         \midrule
         Teacher & \textbf{96.8} & 78.6 & \textbf{93.2} & \textbf{96.9} & 60.7\\
         \midrule
         Spec. & 96.3 & 73.0 &  87.6 & 95.5 & 40.1\\
         Wavlm train & 96.1 & 72.6 & 93.0 & 96.7 & 60.5\\
         Wavlm & \textbf{96.8} & \textbf{79.5} & \textbf{93.1} & \textbf{96.9} & \textbf{61.4} \\
         \bottomrule
    \end{tabular}
    \caption{AragonRadio performance}
    \label{tab:seg_results}
\end{table}

Using Wavlm features as input of the proxy model drastically improves the segmentation performance.
When the NMF dictionary is trained simultaneously as the segmentation task, the proxy model reaches 96.1\% and 96.7\% F1-score on SAD.
The ND performance remains lower than the teachers with a 72.6\% F1-score, which represents an absolute -6\% degradation.
The MD and OSD performances are similar to the teacher with 93.0\% and 60.5\% F1-score respectively.
While showing similar performance as the teacher, training the NMF dictionary degrades noise detection.

When the NMF dictionary is pre-learned, the proxy model delivers similar or even better segmentation performance as the teacher.
The proxy model reaches a 79.5\% F1-score on ND (+0.9\% absolute improvement w.r.t. the teacher), and 61.4\% F1-score on OSD.
This system shows the best segmentation performance among all the models.

The Wavlm-based proxy models deliver the best performance when the dictionary is pre-learned.
Learning a common embedding for classification and spectrogram reconstruction seems easier under these conditions.
This last model is kept for the explanation extraction presented in the following section.
